\bfseries A simple momentum-transport model for sailing

### 2021-07-09 paper/main.tex
dwsign

One might ask: Intuitively, how does upwind travel work?
You can think of the boat like a slippery wedge, with the wind pushing on one side of the wedge (the sail) and the water pushing on the other side of the wedge (the keel).
The wedge slips forward.
Maybe that helps?

@@

In all of the experiments and figures given above, we made use of a model boat with the following effective areas:
\begin{align}
  A_\sail &= XXX\,\mm \\
  A_\keel &= YYY\,\mm \\
  A_\above &= ZZZ\,\mm \\
  A_\below &= QQQ\,\mm ~.
\end{align}
This boat is designed such that $\rho_\air\,A_\sail = \rho_\water\,A_\keel$, which seems sensible, but is perhaps not industry standard.
This boat also has very good drag ratios or lift ratios:
The ratio of effective area of sail to hull-above is 256, as is the ratio of effective area of keel to hull-below.
All these ratios were set not by analyzing any real boats, but by making the velocity curve shown in \figref{fig:hourgood} look reasonable, or accord with our intuitions and expectations.
HOGG: NEED A BETTER NAME THAN VELOCITY CURVE; WHAT IS THIS DIAGRAM CALLED?
Recall, for one, that our boat is a brutal approximation!
For two, these areas are \emph{effective areas} within this brutal approximation, not measured areas.

>>>>

One might ask: Intuitively, how does upwind travel work?
You can think of the boat like a slippery wedge, with the wind pushing on one side of the wedge (the sail) and the water pushing on the other side of the wedge (the keel).
The wedge slips forward.
Maybe that helps?
HOGG SAYS: I THINK WE NEED A DIAGRAM HERE, SHOWING DWFTTW and UW.

@@

In all of the experiments and figures given above, we made use of a model boat with the following effective areas:
\begin{align}
  A_\sail &= XXX\,\mm \\
  A_\keel &= YYY\,\mm \\
  A_\above &= ZZZ\,\mm \\
  A_\below &= QQQ\,\mm ~.
\end{align}
This boat is designed such that $\rho_\air\,A_\sail = \rho_\water\,A_\keel$, which seems sensible, but is perhaps not industry standard.
This boat also has very good drag ratios or lift ratios:
The ratio of effective area of sail to hull-above is 256, as is the ratio of effective area of keel to hull-below.
All these ratios were set not by analyzing any real boats, but by making the velocity curve shown in \figref{fig:hourgood} look reasonable, or accord with our intuitions and expectations.
HOGG: NEED A BETTER NAME THAN VELOCITY CURVE; WHAT IS THIS DIAGRAM CALLED?
Recall, for one, that our boat is a brutal approximation!
For two, these areas are \emph{effective areas} within this brutal approximation, not measured areas.
Probably the least realistic of these effective-area ratios is $A_\keel/A_\below$; probably real boats rarely have this keel lift ratio in the hundreds.
In this sense, maybe our model is more appropriate for an ice yacht than a sailboat?
